Formalized Linear Programming

### 2019-09-23 TeX/paper.tex

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
  Sentence about applications of simplex. Most simplex solvers are non-verified implementations and are not guaranteed to be correct. They are usually written in languages like C++ which are difficult to certify. One verified implementation exists, but it is not intended to be executable in practice. We implement a formally verified executable simplex solver in the Lean theorem prover. Our implementation uses Bland's rule to select a pivot, and a pivot function stated without any matrix multiplication in contrast to some book proofs on the simplex algorithm. This research demonstrates the practicality of Lean as a language for fast verified algorithms.
\end{abstract}

>>>>

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
% What is the general topic we look at?
Correct and efficient linear programming, using the simplex
algorithm, is of high importance not only in the context of
operational research but also in programming language analysis.
% What is the specific research problem we face?
While existing solvers are robust, the lack of formally verified
implementations prevents their use in computational proofs and
rare corner-case bugs make the use of linear programming for
automatic program generation difficult.
% Why has nobody else adequately answered the research problem yet?
Today, existing implementations are either written in low-level
high-performance languages (e.g., C++), which are hard to verify, or
focus on the verification aspects but are not intended to be executable in practice.
% What is our key idea to address the stated research problem?
We address this problem by implementing an executable and verified
simplex solver in the Lean programming language.
% What are the key steps needed to successfully implement our idea?
We ensure both ease of verification and reasonable execution
performance by uses Bland's rule to select a pivot and by stating our
pivot function without large and costly matrix multiplications as
they are often used in textbook formalizations.
% What is the key global impact we envision our research to have?
Our research provides core foundations for verified linear
programming and demonstrates the practicality of Lean as a language
for fast verified constraint programming.

\end{abstract}
